---
title: "AMP-AD Manuscript Analyses"
output: html_notebook
---

Pull targeted genesets

```{r,include =F}
targetedGeneSets <- AMPAD::collateEnrichmentSets()
#str(targetedGeneSets)
```

For each of the three build the data frame of the respective Analyses

```{r,include=FALSE}
targetedEnrichment <- list()
targetedEnrichment$ad <- AMPAD::run_amp_ad_enrichment2(targetedGeneSets$ad,
                                                      'AD',
                                                      hgnc = TRUE,
                                                      manifestId = 'syn11932957')

targetedEnrichment$cell <- AMPAD::run_amp_ad_enrichment2(targetedGeneSets$cell,
                                                        'Cell',
                                                        hgnc= TRUE,
                                                        manifestId = 'syn11932957')

targetedEnrichment$deg <- AMPAD::run_amp_ad_enrichment2(targetedGeneSets$deg,
                                                       'DEG',
                                                       hgnc=FALSE,
                                                       manifestId = 'syn11932957')

targetedEnrichment$degMeta <- AMPAD::run_amp_ad_enrichment2(targetedGeneSets$degMeta,
                                                           'DEGmeta',
                                                           hgnc=FALSE,
                                                           manifestId = 'syn11932957')

targetedEnrichment$targetPathways <- AMPAD::run_amp_ad_enrichment2(targetedGeneSets$targetedPathways,
                                                           'TargetedPathways',
                                                           hgnc=FALSE,
                                                           manifestId = 'syn11932957')

targetedEnrichment$ad_deg <- AMPAD::run_amp_ad_enrichment2_lists(targetedGeneSets$deg,
                                                                 'ADDEG',
                                                                 targetedGeneSets$ad,
                                                                 hgnc = T,
                                                                 testhgnc = F)

targetedEnrichment$ad_degmeta <- AMPAD::run_amp_ad_enrichment2_lists(targetedGeneSets$degMeta,
                                                                 'ADDEGMeta',
                                                                 targetedGeneSets$ad,
                                                                 hgnc = T,
                                                                 testhgnc = F)

targetedEnrichment$degFull <- rbind(targetedEnrichment$deg,targetedEnrichment$ad_deg)
targetedEnrichment$degMetaFull <- rbind(targetedEnrichment$degMeta, targetedEnrichment$ad_degmeta)
```


Add adjusted p-values 

```{r}
targetedEnrichment$ad$adj.pval <- p.adjust(targetedEnrichment$ad$fisherPval,method='fdr')
targetedEnrichment$deg$adj.pval <- p.adjust(targetedEnrichment$deg$fisherPval,method='fdr')
targetedEnrichment$cell$adj.pval <- p.adjust(targetedEnrichment$cell$fisherPval,method='fdr')
targetedEnrichment$degMeta$adj.pval <- p.adjust(targetedEnrichment$degMeta$fisherPval,method='fdr')
targetedEnrichment$targetPathways$adj.pval <- p.adjust(targetedEnrichment$targetPathways$fisherPval,method='fdr')
targetedEnrichment$degFull$adj.pval <- p.adjust(targetedEnrichment$degFull$fisherPval,method='fdr')
targetedEnrichment$degMetaFull$adj.pval <- p.adjust(targetedEnrichment$degMetaFull$fisherPval,method='fdr')
```

Make cell type summary plots

x- axis : module
y- axis fisher-'s odds ratio

```{r}
modMeta <- AMPAD::getModuleMetainfo('syn11932957')
dummyDf <- targetedEnrichment$cell
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
#dummyDf <- dplyr::filter(targetedEnrichment$cell,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf$category <- gsub('Zhang\\.','',dummyDf$category)
dummyDf$category <- factor(dummyDf$category,levels = rev(c('Astrocyte',
                                                       'Endothelial',
                                                       'Microglia',
                                                       'Neuron',
                                                       'MyelinOligos',
                                                       'NewOligos',
                                                       'OPC')))
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
customDf <- data.frame(moduleName=c('TCXblue',
                                      'IFGyellow',
                                      'PHGyellow',
                                      'DLPFCblue',
                                      'CBEturquoise',
                                      'STGblue',
                                      'PHGturquoise',
                                      'IFGturquoise',
                                      'TCXturquoise',
                                      'FPturquoise',
                                      'IFGbrown',
                                      'STGbrown',
                                      'DLPFCyellow',
                                      'TCXgreen',
                                      'FPyellow',
                                      'CBEyellow',
                                      'PHGbrown',
                                      'DLPFCbrown',
                                      'STGyellow',
                                      'PHGgreen',
                                      'CBEbrown',
                                      'TCXyellow',
                                      'IFGblue',
                                      'FPblue',
                                      'FPbrown',
                                      'CBEblue',
                                      'DLPFCturquoise',
                                      'TCXbrown',
                                      'STGturquoise',
                                      'PHGblue'),
                         Cluster= c(rep('Consensus Cluster A',3),
                                       rep('Consensus Cluster B',7),
                                       rep('Consensus Cluster C',7),
                                       rep('Consensus Cluster D',7),
                                       rep('Consensus Cluster E',6)),
                         stringsAsFactors=F)
 dummyDf <- dplyr::left_join(dummyDf,customDf,by=c('Module'='moduleName'))
 dummyDf$Cluster <- factor(dummyDf$Cluster,levels = (c('Consensus Cluster A',
                                                      'Consensus Cluster B',
                                                      'Consensus Cluster C',
                                                      'Consensus Cluster D',
                                                      'Consensus Cluster E')))
dummyDf$Module <- factor(dummyDf$Module,levels = (c('TCXblue',
                                                   'IFGyellow',
                                                   'PHGyellow',
                                                   'DLPFCblue',
                                                   'CBEturquoise',
                                                   'STGblue',
                                                   'PHGturquoise',
                                                   'IFGturquoise',
                                                   'TCXturquoise',
                                                   'FPturquoise',
                                                   'IFGbrown',
                                                   'STGbrown',
                                                   'DLPFCyellow',
                                                   'TCXgreen',
                                                   'FPyellow',
                                                   'CBEyellow',
                                                   'PHGbrown',
                                                   'DLPFCbrown',
                                                   'STGyellow',
                                                   'PHGgreen',
                                                   'CBEbrown',
                                                   'TCXyellow',
                                                   'IFGblue',
                                                   'FPblue',
                                                   'FPbrown',
                                                   'CBEblue',
                                                   'DLPFCturquoise',
                                                   'TCXbrown',
                                                   'STGturquoise',
                                                   'PHGblue')))

 

g <- ggplot2::ggplot(dummyDf,
                     ggplot2::aes(x = Module,
                                  y = category,
                                  size = fisherOR,
                                  color = Cluster))
g <- g + ggplot2::geom_count()
#g <- g + ggplot2::scale_y_log10()

g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
#g <- g + ggplot2::theme(axis.text.x=ggplot2::element_blank(),
#        axis.ticks.x=ggplot2::element_blank())
#g <- g + ggplot2::scale_color_gradientn(colours = c(viridis::viridis(2)[2], viridis::viridis(2)[1]),values = c(0,1), breaks = c(1.5, 3,8,20,50,110),trans='log')
#g <- g + ggplot2::coord_flip()
#g <- g + ggplot2::ggtitle('Enrichment for Cell Type Specific Signatures')
g <- g + ggplot2::labs(y = 'Cell Type Signature',
                       x = 'AD Coexpression Module')

g
ggplot2::ggsave('figure2B.tiff',device='tiff',units='mm',width=85,height=85,scale=1.8)
#ggplot2::ggsave('cell_enrichments.png')
```

overlap table with amp-ad related gene sets
```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf <- dplyr::filter(dummyDf,adj.pval<=0.05)
dummyDf <- dplyr::filter(dummyDf,category == 'Nominated_targets' |
                           category == 'MSSM' | 
                           category == 'Mayo_simple' | 
                           category == 'Mayo_comprehensive' | 
                           category == 'Emory' | 
                           category == 'Columbia_Broad_Rush_m109')
dummyDf <- dplyr::select(dummyDf,
                         Module,
                         category,
                         mod_size,
                         category_size,
                         nInter,
                         adj.pval,
                         fisherOR)

colnames(dummyDf) <- c('Module Name',
                       'AMP-AD Gene Set',
                       'Module Size',
                       'AMP-AD Gene Set Size',
                       'Size of Intersection',
                       'Adjusted P-value',
                       'FET Odds Ratio')
write.csv(dummyDf,file='amp-ad_overlap_stats.csv',quote=F,row.names=F)
```
differential expression meta analysis summary tables
```{r}
dummyDf <- targetedEnrichment$degMetaFull
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf <- dplyr::filter(dummyDf,adj.pval<=0.05)
dummyDf$Module[is.na(dummyDf$Module)] <- dummyDf$ModuleNameFull[is.na(dummyDf$Module)]
dummyDf <- dplyr::select(dummyDf,
                         Module,
                         category,
                         mod_size,
                         category_size,
                         nInter,
                         adj.pval,
                         fisherOR)
colnames(dummyDf) <- c('Module or Gene Set Name',
                       'DEG Gene Set',
                       'Module or Gene Set Size',
                       'DEG Gene Set Size',
                       'Size of Intersection',
                       'Adjusted P-value',
                       'FET Odds Ratio')
dummyDf <- dplyr::arrange(dummyDf,desc(`FET Odds Ratio`))
adUp <- dplyr::filter(dummyDf,`DEG Gene Set` == 'ad.control.random.UP')
adDown <- dplyr::filter(dummyDf,`DEG Gene Set` == 'ad.control.random.DOWN')
adUpMale <- dplyr::filter(dummyDf,`DEG Gene Set` == 'ad.control.MALE.random.UP')
adDownMale <- dplyr::filter(dummyDf,`DEG Gene Set` == 'ad.control.MALE.random.DOWN')
adUpFemale <- dplyr::filter(dummyDf,`DEG Gene Set` == 'ad.control.FEMALE.random.UP')
adDownFemale <- dplyr::filter(dummyDf,`DEG Gene Set` == 'ad.control.FEMALE.random.DOWN')

write.csv(adUp,file='adup.csv',quote=F,row.names=F)
write.csv(adDown,file='adDown.csv',quote=F,row.names=F)
write.csv(adUpMale,file='adUpMale.csv',quote=F,row.names=F)
write.csv(adDownMale,file='adDownMale.csv',quote=F,row.names=F)
write.csv(adUpFemale,file='adUpFemale.csv',quote=F,row.names=F)
write.csv(adDownFemale,file='adDownFemale.csv',quote=F,row.names=F)

#View(dplyr::filter(dummyDf,category == 'ad.control.FEMALE.random.UP'))
```


AD genetics summary
```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
dummyDf$category <- factor(dummyDf$category,
                           levels = rev(c('genecards',
                                       'pantherPresenilin',
                                       'dbgap',
                                       'igap',
                                       'jensenDisease',
                                       'omimExpanded',
                                       'biocarta',
                                       'wikipathwaysMouse',
                                       'wikipathwaysHuman',
                                       'pantherAmyloid',
                                       'kegg',                                       
                                       'omim',
                                       'Nominated_targets',
                                       'MSSM',
                                       'Mayo_simple',
                                       'Mayo_comprehensive',
                                       'Emory',
                                       'Columbia_Broad_Rush_m109')))

 dummyDf <- dplyr::left_join(dummyDf,customDf,by=c('Module'='moduleName'))
dummyDf$Cluster <- factor(dummyDf$Cluster,levels = (c('Consensus Cluster A',
                                                      'Consensus Cluster B',
                                                      'Consensus Cluster C',
                                                      'Consensus Cluster D',
                                                      'Consensus Cluster E')))

dummyDf$Module <- factor(dummyDf$Module,levels = (c('TCXblue',
                                                   'IFGyellow',
                                                   'PHGyellow',
                                                   'DLPFCblue',
                                                   'CBEturquoise',
                                                   'STGblue',
                                                   'PHGturquoise',
                                                   'IFGturquoise',
                                                   'TCXturquoise',
                                                   'FPturquoise',
                                                   'IFGbrown',
                                                   'STGbrown',
                                                   'DLPFCyellow',
                                                   'TCXgreen',
                                                   'FPyellow',
                                                   'CBEyellow',
                                                   'PHGbrown',
                                                   'DLPFCbrown',
                                                   'STGyellow',
                                                   'PHGgreen',
                                                   'CBEbrown',
                                                   'TCXyellow',
                                                   'IFGblue',
                                                   'FPblue',
                                                   'FPbrown',
                                                   'CBEblue',
                                                   'DLPFCturquoise',
                                                   'TCXbrown',
                                                   'STGturquoise',
                                                   'PHGblue')))


# g <- ggplot2::ggplot(dummyDf,
#                      ggplot2::aes(x = Module,
#                                   y = category,
#                                   size = fisherOR,
#                                   color = -log10(adj.pval)))
# g <- g+ggplot2::geom_count()
# #g <- g + ggplot2::scale_y_log10()
# #g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
# g <- g + ggplot2::theme(axis.text.x=ggplot2::element_blank(),
#         axis.ticks.x=ggplot2::element_blank())
# g <- g + ggplot2::scale_color_gradientn(colours = c(viridis::viridis(2)[2], viridis::viridis(2)[1]),values = c(0,1), breaks = c(1.4,6,12,18,25))
# #g <- g + ggplot2::coord_flip()
# g <- g + ggplot2::ggtitle('Enrichment for AD Signatures')

g <- ggplot2::ggplot(dummyDf,
                     ggplot2::aes(x = Module,
                                  y = category,
                                  size = fisherOR,
                                  color = Cluster))
g <- g + ggplot2::geom_count()

g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))

g <- g + ggplot2::labs(y = 'AD Signature',
                       x = 'AD Coexpression Module')
g
ggplot2::ggsave('figure2C.tiff',device='tiff',units='mm',width=85,height=85,scale=1.8)
#ggplot2::ggsave('ad_signature_enrichments.png')
```



```{r}
dummyDf <- targetedEnrichment$ad
dummyDf$fisherOR[dummyDf$adj.pval>=0.05] <- NA
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf<- dplyr::filter(dummyDf,category == 'AMP.AD.Nominated.Targets' |
                                    category == 'AMP.AD.McKenzie.et.al..2017.Red' |
                                    category == 'AMP.AD.McKenzie.et.al..2017.Light.green' |
                                    category == 'AMP.AD.McKenzie.et.al..2017.Green' |
                                    category == 'AMP.AD.Allen.et.al..2018.AD.PSP.TCX40.CS' |
                                    category == 'AMP.AD.Allen.et.al..2018.AD.PSP.TCX10.CS' | 
                                    category == 'AMP.AD.Johnson.et.al..2018.RNA.Binding' | 
                                    category == 'AMP.AD.Mostafavi.et.al..2018.m109')
dummyDf$category[dummyDf$category=='AMP.AD.Nominated.Targets'] = 'Nominated\nTargets'
dummyDf$category[dummyDf$category=='AMP.AD.McKenzie.et.al..2017.Red'] = 'MSSM Oligo\nRed'
dummyDf$category[dummyDf$category=='AMP.AD.McKenzie.et.al..2017.Light.green'] = 'MSSM Oligo\nLight green'
dummyDf$category[dummyDf$category=='AMP.AD.McKenzie.et.al..2017.Green'] = 'MSSM Oligo\nGreen'
dummyDf$category[dummyDf$category=='AMP.AD.Allen.et.al..2018.AD.PSP.TCX40.CS'] = 'Mayo Oligo\nAD.PSP.TCX40.CS'
dummyDf$category[dummyDf$category=='AMP.AD.Allen.et.al..2018.AD.PSP.TCX10.CS'] = 'Mayo Oligo\nAD.PSP.TCX10.CS'
dummyDf$category[dummyDf$category=='AMP.AD.Johnson.et.al..2018.RNA.Binding'] = 'Emory\nRNA binding'
dummyDf$category[dummyDf$category=='AMP.AD.Mostafavi.et.al..2018.m109'] = 'Rush m109'



#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
dummyDf$category <- factor(dummyDf$category,
                           levels = (c('Nominated\nTargets',
                                       'MSSM Oligo\nRed',
                                       'MSSM Oligo\nLight green',
                                       'MSSM Oligo\nGreen',
                                       'Mayo Oligo\nAD.PSP.TCX40.CS',
                                       'Mayo Oligo\nAD.PSP.TCX10.CS',
                                       'Emory\nRNA binding',
                                       'Rush m109')))

 dummyDf <- dplyr::left_join(dummyDf,customDf,by=c('Module'='moduleName'))
dummyDf$Cluster <- factor(dummyDf$Cluster,levels = (c('Astrocytic',
                                                      'Microglial',
                                                      'Neuronal',
                                                      'Oligodendroglial',
                                                      'Proteostasis')))

dummyDf$Module <- factor(dummyDf$Module,levels = rev(c('TCXblue',
                                                   'IFGyellow',
                                                   'PHGyellow',
                                                   'DLPFCblue',
                                                   'CBEturquoise',
                                                   'STGblue',
                                                   'PHGturquoise',
                                                   'IFGturquoise',
                                                   'TCXturquoise',
                                                   'FPturquoise',
                                                   'IFGbrown',
                                                   'STGbrown',
                                                   'DLPFCyellow',
                                                   'TCXgreen',
                                                   'FPyellow',
                                                   'CBEyellow',
                                                   'PHGbrown',
                                                   'DLPFCbrown',
                                                   'STGyellow',
                                                   'PHGgreen',
                                                   'CBEbrown',
                                                   'TCXyellow',
                                                   'IFGblue',
                                                   'FPblue',
                                                   'FPbrown',
                                                   'CBEblue',
                                                   'DLPFCturquoise',
                                                   'TCXbrown',
                                                   'STGturquoise',
                                                   'PHGblue')))


# g <- ggplot2::ggplot(dummyDf,
#                      ggplot2::aes(x = Module,
#                                   y = category,
#                                   size = fisherOR,
#                                   color = -log10(adj.pval)))
# g <- g+ggplot2::geom_count()
# #g <- g + ggplot2::scale_y_log10()
# #g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
# g <- g + ggplot2::theme(axis.text.x=ggplot2::element_blank(),
#         axis.ticks.x=ggplot2::element_blank())
# g <- g + ggplot2::scale_color_gradientn(colours = c(viridis::viridis(2)[2], viridis::viridis(2)[1]),values = c(0,1), breaks = c(1.4,6,12,18,25))
# #g <- g + ggplot2::coord_flip()
# g <- g + ggplot2::ggtitle('Enrichment for AD Signatures')

g <- ggplot2::ggplot(dummyDf,
                     ggplot2::aes(x = Module,
                                  y = category,
                                  size = fisherOR,
                                  color = Cluster))
g <- g + ggplot2::geom_count()

g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))

g <- g + ggplot2::coord_flip()

g <- g + ggplot2::labs(y = 'AD Signature',
                       x = 'AD Coexpression Module')
g
#ggplot2::ggsave('figure2C.tiff',device='tiff',units='mm',width=85,height=85,scale=1.8)
ggplot2::ggsave('amp_ad_new_modules.png',units='in',width=4.91,height=4.8,scale=1.4)
```


```{r}
dummyDf <- dplyr::filter(targetedEnrichment$degMeta,adj.pval<=0.05)
dummyDf <- dplyr::filter(dummyDf,category == 'ad.control.FEMALE.random.DOWN' |
                           category == 'ad.control.FEMALE.random.UP' | 
                           category == 'ad.control.MALE.random.DOWN' | 
                           category == 'ad.control.MALE.random.UP')
dummyDf$adj.pval[dummyDf$adj.pval==0] = 10^-300
dummyDf$category <- gsub('ad\\.control\\.FEMALE\\.random\\.DOWN','Female, Down',dummyDf$category)
dummyDf$category <- gsub('ad\\.control\\.MALE\\.random\\.DOWN','Male, Down',dummyDf$category)
dummyDf$category <- gsub('ad\\.control\\.FEMALE\\.random\\.UP','Female, Up',dummyDf$category)
dummyDf$category <- gsub('ad\\.control\\.MALE\\.random\\.UP','Male, Up',dummyDf$category)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
#dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))
 dummyDf <- dplyr::left_join(dummyDf,customDf,by=c('Module'='moduleName'))
dummyDf$Cluster <- factor(dummyDf$Cluster,levels = (c('Consensus Cluster A',
                                                      'Consensus Cluster B',
                                                      'Consensus Cluster C',
                                                      'Consensus Cluster D',
                                                      'Consensus Cluster E')))
dummyDf$category <- factor(dummyDf$category,rev(c('Female, Up',
                                                  'Male, Up',
                                                  'Female, Down',
                                                  'Male, Down')))
dummyDf$Module <- factor(dummyDf$Module,levels = (c('TCXblue',
                                                   'IFGyellow',
                                                   'PHGyellow',
                                                   'DLPFCblue',
                                                   'CBEturquoise',
                                                   'STGblue',
                                                   'PHGturquoise',
                                                   'IFGturquoise',
                                                   'TCXturquoise',
                                                   'FPturquoise',
                                                   'IFGbrown',
                                                   'STGbrown',
                                                   'DLPFCyellow',
                                                   'TCXgreen',
                                                   'FPyellow',
                                                   'CBEyellow',
                                                   'PHGbrown',
                                                   'DLPFCbrown',
                                                   'STGyellow',
                                                   'PHGgreen',
                                                   'CBEbrown',
                                                   'TCXyellow',
                                                   'IFGblue',
                                                   'FPblue',
                                                   'FPbrown',
                                                   'CBEblue',
                                                   'DLPFCturquoise',
                                                   'TCXbrown',
                                                   'STGturquoise',
                                                   'PHGblue')))

# g <- ggplot2::ggplot(dummyDf,
#                      ggplot2::aes(x = Module,
#                                   y = category,
#                                   size = fisherOR,
#                                   color = -log10(adj.pval)))
# g <- g+ggplot2::geom_count()
# #g <- g + ggplot2::scale_y_log10()
# #g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
# g <- g + ggplot2::theme(axis.text.x=ggplot2::element_blank(),
#         axis.ticks.x=ggplot2::element_blank())
# g <- g + ggplot2::scale_color_gradientn(colours = c(viridis::viridis(2)[2], viridis::viridis(2)[1]),values = c(0,1), breaks = c(1.5, 3,8,20,50,110,300),trans='log')
# #g <- g + ggplot2::coord_flip()
# g <- g + ggplot2::ggtitle('Enrichment for AD DEG Signatures')

g <- ggplot2::ggplot(dummyDf,
                     ggplot2::aes(x = Module,
                                  y = category,
                                  size = fisherOR,
                                  color = Cluster))
g <- g + ggplot2::geom_count()

g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))

g <- g + ggplot2::labs(y = 'DEG Sex Specific Meta Analysis',
                       x = 'AD Coexpression Module')
g
ggplot2::ggsave('figure2D.tiff',device='tiff',units='mm',width=85,height=85,scale=1.8)
#ggplot2::ggsave('deg_signature_enrichments.png')
```

```{r}
#modMeta <- AMPAD::getModuleMetainfo('syn11932957')
dummyDf <- dplyr::filter(targetedEnrichment$targetPathways,adj.pval<=0.05)
dummyDf <- dplyr::left_join(dummyDf,modMeta)
dummyDf$ModuleBrainRegion <- factor(dummyDf$ModuleBrainRegion,levels = unique(dummyDf$ModuleBrainRegion))

g <- ggplot2::ggplot(dummyDf,
                     ggplot2::aes(x = Module,
                                  y = category,
                                  size = fisherOR,
                                  color = -log10(adj.pval)))
g <- g + ggplot2::geom_count()
#g <- g + ggplot2::scale_y_log10()
g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
g <- g + ggplot2::scale_color_gradientn(colours = c(viridis::viridis(2)[2], viridis::viridis(2)[1]),values = c(0,1))
g <- g + ggplot2::coord_flip()

g

```



Reformate DEG results for visualization

```{r}
tcx_keep <- intersect(grep('TCX',targetedEnrichment$deg$ModuleNameFull),
                      grep('TCX',targetedEnrichment$deg$category))
phg_keep <- intersect(grep('PHG',targetedEnrichment$deg$ModuleNameFull),
                      grep('PHG',targetedEnrichment$deg$category))
cbe_keep <- intersect(grep('CBE',targetedEnrichment$deg$ModuleNameFull),
                      grep('CBE',targetedEnrichment$deg$category))
dlpfc_keep <- intersect(grep('DLPFC',targetedEnrichment$deg$ModuleNameFull),
                      grep('DLPFC',targetedEnrichment$deg$category))
stg_keep <- intersect(grep('STG',targetedEnrichment$deg$ModuleNameFull),
                      grep('STG',targetedEnrichment$deg$category))
ifg_keep <- intersect(grep('IFG',targetedEnrichment$deg$ModuleNameFull),
                      grep('IFG',targetedEnrichment$deg$category))
fp_keep <- intersect(grep('FP',targetedEnrichment$deg$ModuleNameFull),
                      grep('FP',targetedEnrichment$deg$category))
deg <- targetedEnrichment$deg[c(tcx_keep,phg_keep,cbe_keep,dlpfc_keep,stg_keep,ifg_keep,fp_keep),]
deg$adj.pval <- p.adjust(deg$fisherPval,method='fdr')
deg <- dplyr::filter(deg,adj.pval<=0.05)
dumfun <- function(x){
  y<-grep('UP',x)
  y2 <- grep('DOWN',x)
  z <- x
  z[y] <- 'Up'
  z[y2] <- 'Down'
  return(z)
}
sexfun <- function(x){
  y<-grep('\\.FEMALE',x)
  y2 <- grep('\\.MALE',x)
  z <- rep('All',length(x))
  z[y] <- 'Female'
  z[y2] <- 'Male'
  return(z)
}
deg <- dplyr::mutate(deg,direction = dumfun(category))
deg <- dplyr::mutate(deg,sex = sexfun(category))
deg <- dplyr::mutate(deg,dirbysex = paste0(direction,'.',sex))
deg <- dplyr::left_join(deg,modMeta)
```
Plot DEG results

```{r}
g <- ggplot2::ggplot(deg,ggplot2::aes(x = Module,
                                      y = fisherOR,
                                      fill = direction))
g <- g + ggplot2::geom_col(position = 'dodge')
g <- g + ggplot2::facet_grid(. ~ sex)
g <- g + ggplot2::scale_y_log10()
g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
g <- g + ggplot2::coord_flip()

g

```


```{r}
degMeta <- targetedEnrichment$degMeta
degMeta$adj.pval <- p.adjust(degMeta$fisherPval,method='fdr')
degMeta <- dplyr::filter(degMeta,adj.pval<=0.05)
dumfun <- function(x){
  y<-grep('UP',x)
  y2 <- grep('DOWN',x)
  z <- x
  z[y] <- 'Up'
  z[y2] <- 'Down'
  return(z)
}
sexfun <- function(x){
  y<-grep('\\.FEMALE',x)
  y2 <- grep('\\.MALE',x)
  z <- rep('All',length(x))
  z[y] <- 'Female'
  z[y2] <- 'Male'
  return(z)
}
degMeta <- dplyr::mutate(degMeta,direction = dumfun(category))
degMeta <- dplyr::mutate(degMeta,sex = sexfun(category))
degMeta <- dplyr::mutate(degMeta,dirbysex = paste0(direction,'.',sex))
degMeta <- dplyr::left_join(degMeta,modMeta)
```
```{r}
ind <- grep('fixed',degMeta$category)
g <- ggplot2::ggplot(degMeta[ind,],ggplot2::aes(x = Module,
                                      y = fisherOR,
                                      fill = category))
g <- g + ggplot2::geom_col(position = 'dodge')
g <- g + ggplot2::facet_grid(. ~ sex)
g <- g + ggplot2::scale_y_log10()
g <- g + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1))
g <- g + ggplot2::coord_flip()

g

```


Overlap plot

```{r}
AMPAD::pairwiseMatrixOfEnrichments('syn11932957')

```
Make PC statistics

```{r}
AMPAD::makePcStatistics('March 2 2018')
```

Run pathway enrichments and push to synapse


```{r}
pathwayGeneSets <- AMPAD::collatePathways()
fullPathwayEnrichmentsList <- mapply(AMPAD::run_amp_ad_enrichment,
                                 pathwayGeneSets,
                                 names(pathwayGeneSets),
                                 MoreArgs = list(hgnc = TRUE,
                                                 manifestId = 'syn11932957'),
                                 SIMPLIFY = FALSE)
fullPathwayEnrichments <- do.call(rbind,fullPathwayEnrichmentsList)
rSynapseUtilities::makeTable(fullPathwayEnrichments,
                             "Aggregate Module Pathway Enrichments March 7 2018",
                             'syn2370594')
```


Diagnose DEG differences
```{r}
load(synapseClient::synGet('syn10496554',version = 10)@filePath)
amp.ad.de.geneSetsNew <- amp.ad.de.geneSets
load(synapseClient::synGet('syn10496554',version = 9)@filePath)
setdiff(amp.ad.de.geneSetsNew$`Diagnosis.Sex.DLPFC.AD-CONTROL.MALE.DOWN`,amp.ad.de.geneSets$`Diagnosis.Sex.DLPFC.AD-CONTROL.MALE.DOWN`)


```


look at glymphatic flow in tcx vs cbe
```{r}
foobar <- AMPAD::pullExpressionAndPhenoWinsorized()
cbe_diag <- foobar$mayoCER$logitDiagnosis
redCBEMatrix <- foobar$mayoCER[,colnames(foobar$mayoCER)%in%targetedGeneSets$targetedPathways$WP1877]
ab <- svd(scale(redCBEMatrix))
plot(as.factor(cbe_diag),ab$u[,2])
summary(lm(ab$u[,3] ~ cbe_diag))
pheatmap::pheatmap(cbind(cbe_diag,redCBEMatrix))

tcx_diag <- foobar$mayoTCX$logitDiagnosis
redTCXMatrix <- foobar$mayoTCX[,colnames(foobar$mayoTCX)%in%targetedGeneSets$targetedPathways$WP1877]
ab2 <- svd(scale(redTCXMatrix))
plot(as.factor(tcx_diag),ab2$u[,1])
summary(lm(ab2$u[,3] ~ tcx_diag))
pheatmap::pheatmap(cbind(tcx_diag,redTCXMatrix))

```



summarize pathway enrichments for neuronal modules down in women
```{r}
neuron <- list()
neuron$cbeyellow <- AMPAD::summarizeModulesNew('aggregateCBEyellowCBE')
neuron$dlpfcyellow <- AMPAD::summarizeModulesNew('aggregateDLPFCyellowDLPFC')
neuron$ifgbrown <- AMPAD::summarizeModulesNew('aggregateIFGbrownIFG')
neuron$phgbrown <- AMPAD::summarizeModulesNew('aggregatePHGbrownPHG')
neuron$stgbrown <- AMPAD::summarizeModulesNew('aggregateSTGbrownSTG')
neuron$tcxgreen <- AMPAD::summarizeModulesNew('aggregateTCXgreenTCX')
neuron$fpyellow <- AMPAD::summarizeModulesNew('aggregateFPyellowFP')

neuron2 <- do.call(rbind,neuron)

```

group by and summarize fisher odd's ratios across the 7 tissue types

```{r}
neuron3 <- neuron2
neuron3$fisherOR[neuron3$fisherOR==Inf] <- 55
foobar2 <- dplyr::group_by(neuron3,category)
foobar3 <- dplyr::summarise(foobar2,nObserved = length(ModuleNameFull),meanOR = mean(fisherOR))


```


summarize neuroinfllmatory modules
```{r}

infl <- list()
infl$tcxblue <- AMPAD::summarizeModulesNew('aggregateTCXblueTCX')
infl$ifgyellow <- AMPAD::summarizeModulesNew('aggregateIFGyellowIFG')
infl$phgyellow <- AMPAD::summarizeModulesNew('aggregatePHGyellowPHG')
infl$dlpfcblue<- AMPAD::summarizeModulesNew('aggregateDLPFCblueDLPFC')
infl$cbeturquoise <- AMPAD::summarizeModulesNew('aggregateCBEturquoiseCBE')
infl$stgblue<- AMPAD::summarizeModulesNew('aggregateSTGblueSTG')
infl$phgturquoise <- AMPAD::summarizeModulesNew('aggregatePHGturquoisePHG')
infl$ifgturquoise <- AMPAD::summarizeModulesNew('aggregateIFGturquoiseIFG')
infl$tcxturquoise <- AMPAD::summarizeModulesNew('aggregateTCXturquoiseTCX')

infl2 <- do.call(rbind,infl)
infl3 <- infl2
infl3$fisherOR[infl3$fisherOR==Inf] <- 55
foobar2 <- dplyr::group_by(infl3,category)
foobar3 <- dplyr::summarise(foobar2,nObserved = length(ModuleNameFull),meanOR = mean(fisherOR))

```
summary oligodendrocyte pathways
```{r}

oligo <- list()
oligo$dlpfcbrown <- AMPAD::summarizeModulesNew('aggregateDLPFCbrownDLPFC')
oligo$stgyellow <- AMPAD::summarizeModulesNew('aggregateSTGyellowSTG')
oligo$phggreen <- AMPAD::summarizeModulesNew('aggregatePHGgreenPHG')
oligo$cbebrown<- AMPAD::summarizeModulesNew('aggregateCBEbrownCBE')
oligo$tcxyellow <- AMPAD::summarizeModulesNew('aggregateTCXyellowTCX')
oligo$ifgblue <- AMPAD::summarizeModulesNew('aggregateIFGblueIFG')
oligo$fpblue <- AMPAD::summarizeModulesNew('aggregateFPblueFP')

oligo2 <- do.call(rbind,oligo)
oligo3 <- oligo2
oligo3$fisherOR[oligo3$fisherOR==Inf] <- 55
foobar2 <- dplyr::group_by(oligo3,category)
foobar3 <- dplyr::summarise(foobar2,nObserved = length(ModuleNameFull),meanOR = mean(fisherOR))

```
Male specific modules

```{r}
proteo <- list()
proteo$cbeblue <- AMPAD::summarizeModulesNew('aggregateCBEblueCBE')
proteo$dlpfcturquoise <- AMPAD::summarizeModulesNew('aggregateDLPFCturquoiseDLPFC')
proteo$tcxbrown <- AMPAD::summarizeModulesNew('aggregateTCXbrownTCX')
proteo$stgturquoise<- AMPAD::summarizeModulesNew('aggregateSTGturquoiseSTG')
proteo$phgblue <- AMPAD::summarizeModulesNew('aggregatePHGbluePHG')


proteo2 <- do.call(rbind,proteo)
proteo3 <- proteo2
proteo3$fisherOR[proteo3$fisherOR==Inf] <- 55
foobar2 <- dplyr::group_by(proteo3,category)
foobar3 <- dplyr::summarise(foobar2,nObserved = length(ModuleNameFull),meanOR = mean(fisherOR))
```
